### 2016-09-02 2016_Proceedings_ISMIR/papers.tex
fixed name of paper

\includepaper{Template-Based Vibrato Analysis in Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}

>>>>

\includepaper{Template-Based Vibrato Analysis of Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}
